Pillar 2 - Topic Modeling

### 2019-01-11 Pillar 2 - Topic Modeling.Rmd
Plot tf-idf

---
title: "Pillar 2 - Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
---

@@

# TF-IDF
## Functions for Generating Barplots and Word Clouds
```{r function make_barplot and make_WC, out.height=8, out.width=16}
make_barplot <- function(data, facet, n_col = 5){

  facet <- enquo(facet)

  g <- data %>%
    rename(facet = !!facet) %>%
    ggplot(aes(reorder_within(word, tf_idf, facet), tf_idf)) +
    geom_col(show.legend = F) +
    labs(x = NULL, y = "tf-idf") +
    scale_x_reordered() +
    facet_wrap(~ facet, scales = "free", ncol = n_col) +
    coord_flip()

  ggsave(paste(facet[2], "_BP.jpeg", sep = ""), path = "Plots")
  return(g)

}

make_WC <- function(data, facet, n_col = 5){

  facet <- enquo(facet)

  g <- data %>%
    rename(facet = !!facet) %>%
    group_by(facet) %>%
    mutate(freq = tf_idf / sum(tf_idf)) %>% # normalization within clusters
    ungroup() %>%
    mutate(angle = 10 * sample(-2:2, n(), replace = T, prob = c(1,1,4,1,1))) %>%

    ggplot(aes(size = freq^0.7, label = word, 
               angle = angle, color = freq^0.7)) +
    geom_text_wordcloud_area(area_corr_power = 1,
                             eccentricity    = 1,
                             rm_outside      = T) +
    scale_radius(range = c(2, 10), limits = c(0, NA)) +
    scale_color_gradient(low = "red", high = "blue") +
    facet_wrap(~ facet, ncol = n_col) + 
      theme(
        strip.text.x     = element_text(),
        panel.background = element_rect(fill = "white"),
        plot.title       = element_text(hjust=0.5)
      )

  ggsave(paste(facet[2], "_WC.jpeg", sep = ""), path = "Plots")
  return(g)
}
```

## Course Level
```{r tf-idf per course}
tdm_top <- d_overview_stem %>%
  filter(`Calendar Year` == "2018-2019") %>%
  count(Code, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Code, n = n) %>%
  filter(n >= 2) %>%
  group_by(Code) %>%
  top_n(10, tf_idf) %>%
  ungroup %>%
  filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) # select 25 courses at random

make_barplot(data = tdm_top, facet = Code)
make_WC(data = tdm_top, facet = Code)
```

## Cluster Level
```{r tf-idf per cluster}
tdm_top <- d_overview_stem %>%
  left_join(select(d_course, Code, Cluster), by = "Code") %>%
  filter(`Calendar Year` == "2018-2019",
         !is.na(Cluster)) %>%
  count(Cluster, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Cluster, n = n) %>%
  filter(n >= 5) %>%
  group_by(Cluster) %>%
  top_n(10, tf_idf) %>%
  ungroup

>>>>

---
title: "Pillar 2 - Topic Modeling"
author: "DARS"
date: "`r Sys.Date()`"
output: 
  github_document:
    toc: TRUE
    fig_heigt: 8
    fig_width: 16
---

@@

# TF-IDF
## Functions for Generating Barplots and Word Clouds

```{r}
compute_tf_idf <- function(data) data %>%
                                   count(Code, word) %>%
                                   bind_tf_idf(term = word, document = Code, n = n)

tf_idf_description <- compute_tf_idf(filter(d_description, `Calendar Year` == "2018-2019"))
tf_idf_overview <- compute_tf_idf(filter(d_overview, `Calendar Year` == "2018-2019"))
tf_idf_manual <- compute_tf_idf(d_manual)
```

```{r function make_barplot and make_WC, out.height=8, out.width=16}
plot_tf_idf <- function(data, facet = Course, top = 10, n_col = 5, plot_id = NULL){

  # Setup
  facet_enquo <- enquo(facet)
  facet_ensym <- ensym(facet)

  # Data

  data <- 
    if(facet_ensym == sym("Course")) data %>%
      filter(Code %in% sample(unique(.$Code), size = n_col^2, replace = F)) %>% # random selection of courses
      rename(facet = Code) %>%
      group_by(facet) %>%
      filter(n >= 2) %>%
      top_n(top, tf_idf) %>%
      ungroup

    else if(facet_ensym == sym("Cluster")) data %>%
      left_join(data, select(d_course, Code, Cluster), by = "Code") %>%
      rename(facet = !!facet_enquo) %>%
      group_by(facet) %>%
      summarise(tf_idf = sum(tf_idf))
      filter(n >= 10) %>%
      top_n(top, tf_idf) %>%
      ungroup

      return(data)

  # Barplot
  g <- data %>%
    ggplot(aes(reorder_within(word, tf_idf, facet), tf_idf)) +
    geom_col(show.legend = F) +
    labs(x = NULL, y = "tf-idf") +
    scale_x_reordered() +
    facet_wrap(~ facet, scales = "free", ncol = n_col) +
    coord_flip()

    ggsave(paste(plot_id, facet_ensym, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
    print(g)

  # Word Cloud
  g <- data %>%
    group_by(facet) %>%
    mutate(freq = tf_idf / sum(tf_idf)) %>% # normalization within clusters
    ggplot(aes(size = freq^0.7, label = word, color = freq^0.7)) +
    geom_text_wordcloud_area(area_corr_power = 1,
                             eccentricity    = 1,
                             rm_outside      = T) +
    scale_radius(range = c(2, 10), limits = c(0, NA)) +
    scale_color_gradient(low = "red", high = "blue") +
    facet_wrap(~ facet, ncol = n_col) + 
    theme(
      strip.text.x     = element_text(),
      panel.background = element_rect(fill = "white"),
      plot.title       = element_text(hjust=0.5)
    )

  ggsave(paste(plot_id, facet_ensym, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

## Course Level
```{r tf-idf per course, out.height=8, out.width=16}
set.seed(123)
plot_tf_idf(tf_idf_description, plot_id = "description_")
set.seed(123)
plot_tf_idf(tf_idf_overview, plot_id = "overview_")
set.seed(123)
plot_tf_idf(tf_idf_manual, plot_id = "manual_")
```

## Cluster Level
```{r tf-idf per cluster}

tdm_top <- d_overview_stem %>%
  left_join(select(d_course, Code, Cluster), by = "Code") %>%
  filter(`Calendar Year` == "2018-2019",
         !is.na(Cluster)) %>%
  count(Cluster, `Calendar Year`, word, sort = T) %>%
  bind_tf_idf(term = word, document = Cluster, n = n) %>%
  filter(n >= 5) %>%
  group_by(Cluster) %>%
  top_n(10, tf_idf) %>%
  ungroup
